Emittance preservation of an electron bunch in a loaded quasi-linear plasma wakefield

### 2017-07-12 Tex/Paper.tex
Updated plots
Some cleanup and plot fix

\section[\label{S:I}]{Introduction}

% interested from SMI/AWAKE
% requirements for AWAKE Run 2

@@

\section[\label{S:M}]{Method}
%- explain analogy of short-bunch, SMI case, by referring to earlier Veronica-papers
%- simulation setup PIC/quickpic OS

@@

\subsection[\label{S:M:Setup}]{Drive Beam Parameters}

@@

\subsection[\label{S:M:Setup}]{Witness Beam Parameters}

@@

\section[\label{S:BL}]{Beam Loading}

%~ Eric's Comments
%~ Sec N: Beam loading [in this section we describe the interesting physics, based on a single parameters set]

@@

\begin{figure}
    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/beamLoading}
    \label{Fig:BeamLoading}
    \caption{Comparison between the unloaded longitudinal e-field (no witness beam) and the loaded e-field along the
        axis. The magnitude of the beam density along the axis is shown for reference. The beams travel towards the
        left. $\xi = z - tc$ is the position in the simulation box. The beam density is in units of plasma density
        $n_{0} = 7\nexp{-14}\unit{cm}^{-3}$.}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/plasmaDenTWake}
    \label{Fig:PlasmaDenTWake}
    \caption{}
\end{figure}

@@

\section[\label{S:PO}]{Parameter Optimisation}

%~ Sec N+1: Parameter optimization, or, parameter scaling [in this section we describe how to optimize the electron
%~ beam, and preferably some scalings]
%~ - how to select electron beam parameters:
%~ - longitudinal parameters bunch length and current (simulations results to show: overloaded/underloaded cases)
%~ - transverse parameters of electron emittance / matching [too large, outside bubble.  Do we see increased head
%~   erosion -> faster decay]?  (simulations results to show: evolution of high emittance vs low emittance cases)
%~ (- plasma density?)

\section[\label{S:D}]{Discussion}
\section[\label{S:C}]{Conclusion}

% discussion of optimal electron beam parameters
% implications for AWAKE Run 2

\bibliography{Bibliography}

% ******************************************************************************************************************** %
\end{document}
% ******************************************************************************************************************** %

>>>>

% ******************************************************************************************************************** %
\section[\label{S:I}]{Introduction}
% interested from SMI/AWAKE
% requirements for AWAKE Run 2
% ******************************************************************************************************************** %

@@

% ******************************************************************************************************************** %
\section[\label{S:M}]{Method}
%- explain analogy of short-bunch, SMI case, by referring to earlier Veronica-papers
%- simulation setup PIC/quickpic OS
% ******************************************************************************************************************** %

@@

% ******************************************************************************************************************** %
\subsection[\label{S:M:Setup}]{Drive Beam Parameters}
% ******************************************************************************************************************** %

@@

% ******************************************************************************************************************** %
\subsection[\label{S:M:Setup}]{Witness Beam Parameters}
% ******************************************************************************************************************** %

@@

% ******************************************************************************************************************** %
\section[\label{S:BL}]{Beam Loading}
%~ Eric's Comments
%~ Sec N: Beam loading [in this section we describe the interesting physics, based on a single parameters set]
% ******************************************************************************************************************** %

\begin{figure}[hbt]
    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/beamLoading}
    \label{Fig:BeamLoading}
    \caption{Comparison between the unloaded longitudinal e-field (no witness beam) and the loaded e-field along the
        axis. The magnitude of the beam density along the axis is shown for reference. The beams travel towards the
        left. $\xi = z - tc$ is the position in the simulation box. The beam density is in units of initial plasma
        density $n_{0} = 7\nexp{-14}\unit{cm}^{-3}$. The bottom plot shows the plasma density for the loaded and
        unloaded case. The plasma depletion region behind the proton bunch has a minimum of $67.4\%$ of $n_{0}$. }
\end{figure}

\begin{figure}[hbt]
    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/plasmaDenTWake}
    \label{Fig:PlasmaDenTWake}
    \caption{The plasma density in grey with the proton beam (blue) and the electron beam (red) superimposed. The line
        plot indicates the transverse wakefield $W_{x}(\xi,x) = E_{\xi}(z,x) - B_{y}(\xi,x)$ evaluated at
        $+1\sigma_{eb}$ from the axis.}
\end{figure}

@@

@@

@@

% ******************************************************************************************************************** %
\section[\label{S:PO}]{Parameter Optimisation}
%~ Sec N+1: Parameter optimization, or, parameter scaling [in this section we describe how to optimize the electron
%~ beam, and preferably some scalings]
%~ - how to select electron beam parameters:
%~ - longitudinal parameters bunch length and current (simulations results to show: overloaded/underloaded cases)
%~ - transverse parameters of electron emittance / matching [too large, outside bubble.  Do we see increased head
%~   erosion -> faster decay]?  (simulations results to show: evolution of high emittance vs low emittance cases)
%~ (- plasma density?)
% ******************************************************************************************************************** %

% ******************************************************************************************************************** %
\section[\label{S:D}]{Discussion}
% ******************************************************************************************************************** %

% ******************************************************************************************************************** %
\section[\label{S:C}]{Conclusion}
% discussion of optimal electron beam parameters
% implications for AWAKE Run 2
% ******************************************************************************************************************** %

% ******************************************************************************************************************** %
\bibliography{Bibliography}
\end{document}
% ******************************************************************************************************************** %
